Exposure Consequences - Statistics and Figures

### 2018-02-07 ManuscriptMaterials.Rmd
adressed some of Ahmed's comments

    1. Additionally, since predictions should not be updated in exposure training, but active localization might be evoking a slightly larger shift, this indicates a non-Bayesian process of combining predictions and perceptions in this case.

@@

    3. Within the workspace however, there is no interaction between movement type and training group. Perhaps there is a small update of predicted proprioceptive consequences, that we can't parcel out. A more computational approach would be needed to see if this can explain the pattern of results here.

3. Recalibrated proprioception can reliably predict reach aftereffects, but only after **exposure** training and for _active localization_. This means that recalibrated proprioception indeed leads to motor changes.

    1. There is also a trend towards significance for _passive localization_ to predict reach aftereffects after **classic training**. Perhaps active localization is more similar to no-cursor reaches after exposure training, as both of these can only use recalibrated proprioception as well as updated predictions of proprioceptive consequences. This does not explain the trend towards significance for predicting classic reach aftereffects with passive localization. However, a step-wise multiple regression favours an intercept model for classic reach aftereffects, and a model that mostly relies on active localization for exposure reach aftereffects. So perhaps not too much should be read into the trend towards significance in the correlation. On the other hand, the exposure group had twice as much data, so that the estimated recalibration would be more reliable within each participant. Perhaps with higher quality estimates of proprioceptive recalibration those would be able to predict part of the reach aftereffects even after classic training.

>>>>

    1. Additionally, since predictions should not be updated in exposure training, active localization could have resulted in a _lower_ shift in localization if hand location were estimated by combining recalibrated proprioception and updated prediction in a maximum likelihood way. If anything however, active localization is slightly larger (non-significant) than passive localization. This indicates a non-Bayesian process of combining predictions and perceptions -- in this case.

@@

    3. Within the workspace however, there is no interaction between movement type and training group (but there is a trend if hand angle is used as a random effect, in all analyses the 15 degree data is omitted as Denise said). Perhaps there is a small update of predicted proprioceptive consequences, that we can't parcel out. A more computational approach would be needed to see if this can explain the pattern of results here.

3. Recalibrated proprioception can somewhat predict reach aftereffects, but only after **exposure** training and for _active localization_. This indicates that in some circumstances, recalibrated proprioception might drive motor changes. However, it is possible that the active component of the localization is crucial here. Perhaps exposure training leads to some updates in predicted sensory consequences after all -- be they visual or proprioceptive. These would also factor into the reach aftereffects.

    1. There is also a trend towards significance for _passive localization_ to predict reach aftereffects after **classic training**. Perhaps active localization is more similar to no-cursor reaches after exposure training, as they both use recalibrated proprioception as well as updated predictions of sensory consequences -- which could mostly be proprioceptive consequences after exposure training. This does not explain the trend towards significance for predicting classic reach aftereffects with passive localization. A step-wise multiple regression favours an intercept model for classic reach aftereffects, hence none of the localization data was deemed informative. The same algorithm arrived at a model using active localization to predict exposure reach aftereffects. The intercept model for classic reach aftereffects could signify that not too much should be read into the trend towards significance in the correlation. On the other hand, the exposure group had twice as much data, so that the estimated recalibration would be more reliable within each participant. Perhaps with higher quality estimates of proprioceptive recalibration those would be able to predict part of the reach aftereffects even after classic training.
